\documentclass{sigchi}

% Use this section to set the ACM copyright statement (e.g. for
% preprints).  Consult the conference website for the camera-ready
% copyright statement.

% Copyright
%\CopyrightYear{2020}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
%\doi{https://doi.org/10.1145/3313831.XXXXXXX}
% ISBN
% \isbn{978-1-4503-6708-0/20/04}
%Conference
\conferenceinfo{CHI'20,}{April  25--30, 2020, Honolulu, HI, USA}
%Price

% Use this command to override the default ACM copyright statement
% (e.g. for preprints).  Consult the conference website for the
% camera-ready copyright statement.

%% HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP --
%% Please note you need to make sure the copy for your specific
%% license is used here!
% \toappear{
% Permission to make digital or hard copies of all or part of this work
% for personal or classroom use is granted without fee provided that
% copies are not made or distributed for profit or commercial advantage
% and that copies bear this notice and the full citation on the first
% page. Copyrights for components of this work owned by others than ACM
% must be honored. Abstracting with credit is permitted. To copy
% otherwise, or republish, to post on servers or to redistribute to
% lists, requires prior specific permission and/or a fee. Request
% permissions from \href{mailto:Permissions@acm.org}{Permissions@acm.org}. \\
% \emph{CHI '16},  May 07--12, 2016, San Jose, CA, USA \\
% ACM xxx-x-xxxx-xxxx-x/xx/xx\ldots \$15.00 \\
% DOI: \url{http://dx.doi.org/xx.xxxx/xxxxxxx.xxxxxxx}
% }

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}       % to better equalize the last page
\usepackage{graphics}      % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}   % for umlauts and other diaeresis
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdflang={en-US},pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}


% Some optional stuff you might like/need.
\usepackage{microtype}        % Improved Tracking and Kerning
% \usepackage[all]{hypcap}    % Fixes bug in hyperref caption linking
\usepackage{ccicons}          % Cite your images correctly!
% \usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of
% your draft document, you have to enable the "chi_draft" option for
% the document class. To do this, change the very first line to:
% "\documentclass[chi_draft]{sigchi}". You can then place todo notes
% by using the "\todo{...}"  command. Make sure to disable the draft
% option again before submitting your final document.
\usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{Project Spellda}
\def\plainauthor{James Nail, Logan Brown, Steven Gray}
\def\emptyauthor{}
\def\plainkeywords{Authors' choice; of terms; separated; by
  semicolons; include commas, within terms only; this section is required.}
\def\plaingeneralterms{Documentation, Standardization}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{
    \def\UrlFont{\sf}
  }{
    \def\UrlFont{\small\bf\ttfamily}
  }}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  pdfdisplaydoctitle=true, % For Accessibility
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
  hypertexnames=false
}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{\plaintitle}

\numberofauthors{3}
\author{%
  \alignauthor{James Nail\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{Logan Brown\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
  \alignauthor{Steven Gray\\
    \affaddr{City, Country}\\
    \email{e-mail address}}\\
}

\maketitle

\begin{abstract}
Our project is Project Spellda, a two-dimensional, top down role playing game developed in Godot. Our game will minimally include 3 different levels: a tutorial level to introduce the mechanics of the game, followed by an overworld and dungeon that are intertwined. At the beginning of the game, the player will choose two of the four in-game elements: Fire, Water, Air, and Earth. The player then explores the surrounding area, looking for upgrades to their default spells. At any time, the player can dip into the dungeon to test their abilities on the stronger enemies that await them, with the end goal being to get to the center of the dungeon and slay the boss. The game is made entirely using Godot's built-in scripting language GDScript.
\end{abstract}


% Author Keywords
\keywords{\plainkeywords}



\section{Introduction}

Project Spellda is a top-down 2D arcade style RPG game, mixing elements from the likes of Legend of Zelda among other dungeon crawlers
and RPGs of the era. The style of the game came from the games "Thomas Was Alone" and "Illumine". The game will have an overworld with a couple 
different enemy types, along with several offshoot dungeon-like areas
and one main dungeon existing under the overworld.  The dungeon will be relatively harder than the overworld, with better loot and harder
bosses, as well as mechanics used in the dungeon-like offshoots found scattered in the overworld.  The overworld will have varied difficulties
across numerous zones, with several of these difficulties tying directly to difficulties found within the dungeon.\\\\
	
The main feature of the game is the lighting style, which keeps anything that isn't in direct line of sight pitch black. This makes for interesting
ways to explore areas around you, never knowing what is around the next corner.



\section{Technical Specifications}

We are using the Godot game engine\cite{godot}, with much of our scripting done in a built in language built specfic to the engine; GDScript (Godot Script).
This language is very similar to Python, and has everything you need to use the engine to its fullest. This language even has specific commands for just
the engine, which makes things very customizable.

For Spriting, most of that was made in MS Paint. The simple measuring tools made it easy to have properly sized sprites that stuck to the simplistic art style
we were shooting for in this project.

Some of our knowledge came from a wonderful playlist on youtube (from the youtuber "jmbiv"\cite{jmbiv}), showing how to do certain things so we could translate that knowledge to our project.



\section{Motivations}

Why did we choose to make a video game for our final project? Well, the answer is simple. Each of us had little experience in complete game design, but we were all avid gamers that were eager
to learn what goes into the titles we all know and love. We saw this as a common point of interest and pursued it. Though, this wasn't the first idea that was floated around.

Early on in deciding what to make, there were a few thoughts. Minecraft modding was a possibility, but we all agreed that coding into something that already exists could be more trouble than
it's worth to figure out. Once that was ruled out, outright game developement was suggested and was a favorite. We eventually settled to use the Godot game engine, but only knew roughly that
we wanted a game with magic in it.



\section{Game Overview}

Once we had a general idea of what we wanted to use for game-making, we started to iron out details. So, we made an outline of what we wanted in the game.

The first thing we wanted was three different areas that the player could explore; A tutorial, an overworld, and a dungeon. The tutorial are would be, of course,
a small place that players could learn in and test controls in. The overworld would be a larger area, in which the player would explore and get into all kinds of
trouble. The dungeon was to be the final place the player would encounter, and have trials fitting for someone who had made it thus far.

Secondly, we wanted a minimum of 4 types of enemies. We generally categorized this further by saying we wanted two melee enemies and two ranged enemies. While
we had no specific ideas, we were thinking of having it so that enemies would be designed as simple shapes.

Third, we wanted the player to have the option of 4 different elements to use in spellcasting. To clarify; the player can only have two spells at a time, but they
get to choose two from a pool of four. This was just our starting point, as the four basic elements (water, fire, earth, air) were the first things to pop to mind.
We considered that in the future we could add different, not-so-common types of magic to the game.

Finally, we wanted different puzzles and "offshoot" areas that would encourage the player to explore around the maps and really find everything they can. This was
really from our own experiences as players, making sure that there was plenty to do that was interesting in this game.



\section{Inpirations}
Write about Zelda, Thomas Was Alone, and Illumine here.



\section{Changes from Initial Design}
Write about more foucus on dungeons, puzzles, and aesthetics! Lighting should probably be here too, along with cool particle facts!



\section{Bumps We Hit Along the Way}
We can all write about how stinky Vector movement is, and how our specific tasks were challenging otherwise.



\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}
